The kinematics of the Local Group in a cosmological context

### 2013-01-12 paper/ms.tex
improved discusion on lambda parameter

In complete analogy to the spin parameter, $\lambda$, used to describe dark matter halos, we define the same parameter for halo pairs. This quantity combines into a single scalar the energy and the angular momentum allowing us to make an even more straightforward comparison between the results allowed for observations an the expectations in $\Lambda$CDM. The precise definition of the dimensionless $\lambda$ parameter is the following

@@

where the $\mu=m_{\rm M31}m_{\rm MW}/M)$ is the reduced mass for the pair.

@@

Both panels tell in a clear way the same story as the $e_{\rm tot}-l_{\rm orb}$ plane.

\subsection{Environment}

@@

The data and codes that allow the results of this paper to be reproduced can be found as a github repository {\texttt https://github.com/forero/LG\_Kinematics/}

>>>>

{\bf In complete analogy to the spin parameter used to describe dark matter halos, we define the same parameter, $\lambda$, for halo pairs. This quantity combines into a single scalar the energy and the angular momentum allowing us to make an even more straightforward comparison between the results allowed for observations an the expectations in $\Lambda$CDM. The precise definition of the dimensionless $\lambda$ parameter is the following
}

@@

where the $\mu=m_{\rm M31}m_{\rm MW}/M$ is the reduced mass for the pair.

@@

Both panels in Figure \ref{fig:lambda} tell in a clearer way the story sketched in Figure \ref{fig:EJ} on the $e_{\rm tot}-l_{\rm orb}$ plane. The expected configuration in energy and angular momentum of the LG is slightly inconsistent with the expectation from halo pairs in $\Lambda CDM$.

In terms of the reduced spin parameter $\lambda$ seems to be lower in the LG than expected from LCDM. In the case where the pairs are restricted to have the same total mass and separation as the observational constraints, the reduced energy $e_{\rm tot }$ in the simulation are by construction in the same range as observations. The disagreement must come from the values in the reduced orbital angular momentum $j_{\rm orb}$ which is lower in the observations than the $\Lambda$CDM expectation, but still they are broadly consistent due to the large observational uncertainties.

Figure \ref{fig:lambda} also shows the results from the three constrained simulations. The

@@

The data and codes needed to reproduce the results of this paper can be found as a github repository {\texttt https://github.com/forero/LG\_Kinematics/}.
